Interactive Markdown to explore Clustering

### 2017-06-28 src/ClusterComparison.Rmd
updates on clust comparison

```{r echo=FALSE, message=FALSE}
library(scran)
library(dplyr)
library(gtools)
library(knitr)
library(ggplot2)
library(dynamicTreeCut)
library(Rtsne)
library(pheatmap)
source("functions.R")

rnd_seed <- 300
clustDat <- readRDS("../data/Robjects/ClusterComparison.rds") 
bootDat <- readRDS("../data/Robjects/ClusterBootstrap.rds")
dataList <- readRDS("../data/Robjects/ExpressionList_QC.rds")

#Commence
m <- dataList[[1]]
pD <- dataList[[2]]
fD <- dataList[[3]]
#Gene and Cell filtering
m <- m[fD$keep,pD$PassAll]
pD <- pD[pD$PassAll,]
fD <- fD[fD$keep,]
#Normalization
m <- t(t(m)/pD$sf)
#Identification of HVG 
# fD <- mutate(fD, meanExpression=rowMeans(m),
#              CV2= apply(m,1,cv2))
# 
# genes2lbl <- c("Acta2", "Krt18", "Csn2", "Wap","Krt14")
# lblDat <- filter(fD, symbol %in% genes2lbl)
# V3 <- ggplot(arrange(fD,highVar), aes(x=meanExpression,y=CV2, color=highVar)) +
#     geom_label(data=lblDat, aes(x=meanExpression, y=CV2, label=symbol), nudge_y=0.1) +
#     geom_point(data=lblDat, aes(x=meanExpression, y=CV2), pch=1, size=4) +
#     geom_point(alpha=0.8) +
#     scale_x_log10() +
#     scale_y_log10() +
#     theme_bw()
# V3

#Average Linkage appears to best capture the dendrogram

clustDat <- filter(clustDat, Statistic=="Average Silhouette Width")
compPlot <- ggplot(clustDat, aes(x=as.character(DeepSplit), y=Value, color=Linkage,
			    group=Linkage)) +
geom_path() +
geom_point(aes(size=K)) +
facet_grid(.~Dissimilarity, scales="free_y") +
ylab("Average Silhouette Width") +
compPlot

#Which Linkage is best
m.sub <- m[fD$highVar,]
# trafM <- log2(m.sub+1)
# dms <- c("pearson","spearman","euclidean")
# res <- NULL
# for (dm in dms) {
# Dissimilarity Measure
#     if(dm!="euclidean") {
#     dis <- as.dist((1-cor(trafM,method=dm)))
#     } else {
#         dis <- dist(t(trafM),method=dm)
#     }
# 
# Hierarchical Clustering
#     htree.average <- hclust(dis, method="average")
#     htree.single <- hclust(dis, method="single")
#     htree.complete <- hclust(dis, method="complete")
#     htree.ward <- hclust(dis, method="ward.D2")
# 
#     ccc.average <- cor(cophenetic(htree.average),dis)
#     ccc.single <- cor(cophenetic(htree.single),dis)
#     ccc.complete <- cor(cophenetic(htree.complete),dis)
#     ccc.ward <- cor(cophenetic(htree.ward),dis)
# 
#     tmp <- data.frame("Linkage"=c("Average",
#                                          "Single",
#                                          "Complete",
#                                          "Ward.D2"),
#                              "Cophenetic Correlation Coefficient"=
#                                  c(ccc.average,ccc.single,
#                                    ccc.complete,ccc.ward),
#                              "Dissimilarity"=dm)
#     res <- rbind(res,tmp)
# }
# kable(res)

@@

	   selectInput("lk", label = "Linkage",
		       choices=c("average","complete","single","ward.D2"), selected="average")
	  )

#Visualize Dendrograms
clustering <- reactive({
    dis <- asDis(m.sub,dm=input$dm)
    dynamicCluster(dis, lk=input$lk,
			ds=as.numeric(input$ds),
			output="Cluster",
			minSize=15)
})

renderTable({
    clust <- clustering()
    x <- table(clust$cluster,pD$Condition)
    out <- data.frame("Cluster"=rownames(x),
	       "Virgin"=unname(x[,"NP"]),
	       "Pregnant"=unname(x[,"G"]),
	       "Lactation"=unname(x[,"L"]),
	       "Involution"=unname(x[,"PI"]))
})

renderPlot({
    clust <- clustering()
    nclust <- length(unique(clust$cluster))
    palette(rainbow(nclust))
    htreeWithBars(clust,pD)
}, width=2000, height=900)

renderPlot({
    clust <- clustering()
    nclust <- length(unique(clust$cluster))
    pD$cluster <- factor(clust$cluster)
    tsnPlot <- ggplot(pD, aes(x=tSNE1, y=tSNE2, color=cluster, shape=Replicate)) +
	geom_point(size=4) +
	scale_color_discrete(rainbow(nclust))+
	theme_bw()
    tsnPlot
}, width=800, height=800)

renderPlot({
    clust <- clustering()
    nclust <- length(unique(clust$cluster))
    palette(rainbow(nclust))
    slct <- paste(input$dm,input$lk,input$ds,sep="_")
    boot <- bootDat[[slct]]$bootresult
    boxplot(t(boot),ylim=c(0,1),col=c(1:nclust))

}, width=800, height=800)

renderPlot({
    library(cluster)
    clust <- clustering()
    nclust <- length(unique(clust$cluster))
    palette(rainbow(nclust))
    sils  <- silhouette(x=clust$cluster,dist=clust$dis)
    plot(sils,col=c(1:length(unique(clust$cluster))), border=NA)

}, width=1000, height=1800)

renderPlot({
    clust <- clustering()
    pD$cluster <- clust$cluster
    nclust <- length(unique(clust$cluster))
    ord <- arrange(pD, cluster) 
    simMat <- asSim(clust$dis)
    simMat.ord <- as.matrix(simMat)[as.character(ord$barcode),
				    as.character(ord$barcode)]
    library(pheatmap)
    annoCol <- data.frame("cluster"=as.factor(ord$cluster),
			  "Condition"=ord$Condition)
    rownames(annoCol) <- as.character(ord$barcode)
    ann_colors <- list("cluster"=rainbow(nclust))
    names(ann_colors$cluster) <- c(min(ord$cluster):max(ord$cluster))
    pheatmap(simMat.ord,
	     cluster_rows=FALSE,
	     cluster_cols=FALSE,
	     show_rownames=FALSE,
	     show_colnames=FALSE,
	     annotation_col=annoCol,
	     annotation_colors=ann_colors)
}, width=1200, height=1200)

renderPlot({
    clust <- clustering()
    pD$cluster <- clust$cluster

    genes <- c("Acta2","Csn3","Epcam","Krt8")
	 plotGeneDist(m, pD, fD, genes, colorBy="cluster")
   }, width=1000, height=1000)

@@

renderPlot({
    clust <- clustering()
    pD$cluster <- clust$cluster

>>>>

```{r echo=FALSE, message=FALSE}
library(scran)
library(dplyr)
library(gtools)
library(knitr)
library(ggplot2)
library(reshape2)
library(pheatmap)
source("functions.R")

clustDat <- readRDS("../data/Robjects/secondRun_2500/ClusterComparison.rds") 
# bootDat <- readRDS("../data/Robjects/ClusterBootstrap.rds")
dataList <- readRDS("../data/Robjects/secondRun_2500/ExpressionList_QC_norm.rds")
set.seed(300)
dataList <- subSample(dataList,cell.number=1000)

#Commence
m <- dataList[["counts"]]
pD <- dataList[["phenoData"]]
fD <- dataList[["featureData"]]
rm(dataList)

#Gene and Cell filtering
m <- m[fD$keep,pD$PassAll]
pD <- pD[pD$PassAll,]
fD <- fD[fD$keep,]
#Normalization
m <- t(t(m)/pD$sf)

clustStats <- unlist(clustDat, recursive=FALSE)
clustStats <- clustStats[grepl("Statistics",names(clustStats))]
clustStats <- do.call(rbind,clustStats)

clustStats <- filter(clustStats, Statistic=="Average Silhouette Width")
compPlot <- ggplot(clustStats, aes(x=as.character(DeepSplit), y=Value, color=Linkage, group=Linkage)) +
    geom_path() +
    geom_point(aes(size=K)) +
    facet_grid(.~Dissimilarity, scales="free_y") +
    ylab("Average Silhouette Width")

compPlot

@@

	   selectInput("lk", label = "Linkage",
		       choices=c("average"), selected="average")
	  )

#Visualize Dendrograms
clustering <- reactive({
    lbl <- paste(input$dm,input$lk,input$ds,sep="_")
    cluss <- clustDat[[lbl]][["Labels"]]
})

renderTable({
    clust <- clustering()
    x <- table(clust,pD$Condition)
    out <- data.frame("Cluster"=rownames(x),
	       "Virgin"=unname(x[,"NP"]),
	       "Pregnant"=unname(x[,"G"]),
	       "Lactation"=unname(x[,"L"]),
	       "Involution"=unname(x[,"PI"]))
})

renderPlot({
    clust <- clustering()
    nclust <- length(unique(clust))
    pD$cluster <- factor(clust)
    tsnPlot <- ggplot(pD, aes(x=tSNE1, y=tSNE2, color=cluster, shape=Replicate)) +
	geom_point(size=4) +
	scale_color_discrete(rainbow(nclust))+
	theme_bw()
    tsnPlot
}, width=800, height=800)

# renderPlot({
    #     clust <- clustering()
    #     nclust <- length(unique(clust))
    #     palette(rainbow(nclust))
    #     slct <- paste(input$dm,input$lk,input$ds,sep="_")
    #     boot <- bootDat[[slct]]$bootresult
    #     boxplot(t(boot),ylim=c(0,1),col=c(1:nclust))
    # 
# }, width=800, height=800)

# renderPlot({
#     library(cluster)
#     clust <- clustering()
#     nclust <- length(unique(clust$cluster))
#     palette(rainbow(nclust))
#     sils  <- silhouette(x=clust$cluster,dist=clust$dis)
#     plot(sils,col=c(1:length(unique(clust$cluster))), border=NA)
# 
# }, width=1000, height=1800)

# renderPlot({
#     clust <- clustering()
#     pD$cluster <- clust
#     nclust <- length(unique(clust))
#     ord <- arrange(pD, cluster) 
#     simMat <- asSim(clust$dis)
#     simMat.ord <- as.matrix(simMat)[as.character(ord$barcode),
#                                     as.character(ord$barcode)]
#     library(pheatmap)
#     annoCol <- data.frame("cluster"=as.factor(ord$cluster),
#                           "Condition"=ord$Condition)
#     rownames(annoCol) <- as.character(ord$barcode)
#     ann_colors <- list("cluster"=rainbow(nclust))
#     names(ann_colors$cluster) <- c(min(ord$cluster):max(ord$cluster))
#     pheatmap(simMat.ord,
#              cluster_rows=FALSE,
#              cluster_cols=FALSE,
#              show_rownames=FALSE,
#              show_colnames=FALSE,
#              annotation_col=annoCol,
#              annotation_colors=ann_colors)
# }, width=1200, height=1200)

renderPlot({
    pD$cluster <- clustering()
    genes <- c("Acta2","Csn3","Epcam","Krt8")
	 plotGeneDist(m, pD, fD, genes, colorBy="cluster")
   }, width=1000, height=1000)

@@

renderPlot({
    pD$cluster <- clustering()
